The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-23 outputs/paper/paper.qmd
Update paper to include the replication link

---
title: "The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S."
author: 
  - Sagith Kalaichelvam
  - Youngho Kim
  - Joseph Chung
thanks: "Code, data and reproduction package are available at: https://github.com/UtopianYoungChung/Paper2 and https://doi.org/10.1257/jep.36.1.151"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper explores several potential explanatory factors for the steep decline in birth rates in the United States between 2007 and 2020. The decline in U.S. birthrates offers some significant insights into U.S. society. Changes in birth patterns among recent young adult women moving through the childbearing age group can be directly related to the decline in birth rate from a purely statistical standpoint. We provide evidence that the steep drop in birth rates could be attributed to recent young adults' shifting interests. These shifting priorities represent changes in young adults' preferences regarding having children and aspirations for life. Resonating with the original paper, we conclude with a brief discussion of the implications of the declining birth rate in the United States and its impact on society as an entirety."
    toc: true
    number-sections: true
    colorlinks: true
    lot: true
    lof: true
bibliography: references.bib
---

>>>>

---
title: "The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S."
author: 
  - Sagith Kalaichelvam
  - Youngho Kim
  - Joseph Chung
thanks: "Code, data are available at: https://github.com/UtopianYoungChung/Paper2 and https://doi.org/10.1257/jep.36.1.151 and replication package at: https://doi.org/10.48152/ssrp-cdf6-2r92"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper explores several potential explanatory factors for the steep decline in birth rates in the United States between 2007 and 2020. The decline in U.S. birthrates offers some significant insights into U.S. society. Changes in birth patterns among recent young adult women moving through the childbearing age group can be directly related to the decline in birth rate from a purely statistical standpoint. We provide evidence that the steep drop in birth rates could be attributed to recent young adults' shifting interests. These shifting priorities represent changes in young adults' preferences regarding having children and aspirations for life. Resonating with the original paper, we conclude with a brief discussion of the implications of the declining birth rate in the United States and its impact on society as an entirety."
    toc: true
    number-sections: true
    colorlinks: true
    lot: true
    lof: true
bibliography: references.bib
---
